Linting Linearity in Core/System FC

### 2023-01-02 report.tex
Expand a bit on the Haskell section

\mypara{Linear Types}

@@

@@

>>>>

% \mypara{Linear Types}
\subsection{Linear Types}

@@

Haskell is a functional programming language defined by the "Haskell
Report"\cite{jones1999haskell,marlow2010haskell} and whose \emph{de-facto}
implementation is GHC, the Glasgow Haskell Compiler\cite{GHC}. Haskell is a
\emph{non-strict}, \emph{purely functional} language, i.e., functions cannot
have side effects or mutate data, and contrary to many programming languages,
arguments are \emph{not} evaluated when passed to functions, but rather are only
evaluated when the value is needed.

A function to compute the length of a list in Haskell is defined by pattern
matching on the list and returning $0$ if the list is empty and adding one to
the (computed recursively) length of the rest of the list otherwise. The
following snippet defines the said \textbf{length} function.
\begin{code}
    length [] = 0
    length (x:xs) = 1 + length xs
\end{code}
The function \textbf{length} receives a list and returns an integer, and since
it treats all list's elements the same, it is said to be polymorphic over the
list's elements type. In Haskell, function signatures typically appear above the
definition, and for this particular function we'd have
\begin{code}
    length :: [a] -> Int
\end{code}
where \textbf{a} is a universally quantified type variable, that is,
\textbf{length} can be called on lists of ints, lists of characters, lists of
lists of strings, lists of anything.

The laziness evaluation strategy entails expressions are only evaluated when
needed. If we were to call just the above function on a list of computationally
expensive elements, such as
\begin{code}
    length [5^1234, 6^4567, 8^(9^42)]
\end{code}
We would get the result 3 instantaneously: the elements of the list would never
be evaluated because the \textbf{length} function does not require the value of
each element to compute a result.

% TODO:
Is it outside the scope of this report to discuss the merits and disadvantages
of laziness and purely functional properties? Não estou nada contente com esta
secção em geral. Acho que preciso de escrever o resto para conseguir alguma
coerência.

Another defining feature of Haskell is its powerful type system....

@@

\section{Rust}

They have a linearly typed something?
